---
title: "Function Practice"
author: "Eva Juengling Bean"
format: html
editor: visual
---


```{r}
#| label: libraries
#| echo: false
#| messages: false

library(here)
library(tidyverse)
library(ggplot2)
library(janitor)
```

##Simpson Diversity Function

This function calculates the biodiversity index of a specific area, given the 
total number of species and the number of individuals in each species. Lower
index values are associated with lower diversity.

param (input): n_i is the number of individuals of each species
param (input): N is the total number of species
output/return: diversity value (D)

```{r}
#| label: function
#| echo: true

# making my data
species <- as.factor(c("rabbit", "squirrel", "snake", "gopher", "snail"))
obs <- sample(1:100, 5)

data <- data.frame(species, obs)

# because this function is a sum of the values associated with each species, I
# decided to run the function in a for loop :)

for (i in 1:length(species)){
  simpson.div(n_i=data$obs[i], N=sum(data$obs))
}

# return output
div
```
